The main purpose of SafeStreets is to create a software that provides users the possibility to notify	
authorities	when parking violations occur providing some useful features such as finding the most unsafe areas around them and proposing suggestions to the municipality. In addition, SafeStreets will enable the Local Police to generate traffic tickets from it and to cross all the information it owns with the data of the accidents happened.\\
Specifically, we want to realize a product which is able to:
\begin{itemize}
	
	\item Retrieve pictures uploaded by users of parking violations with possible attached information such as license plate position in the image, type of violation and GPS meta-data.
	
	\item Automatically complete the data of a reported violation running a recognition algorithm able to read license plate text.
	
	\item Thanks to the Computer Vision, recognize useful details such as car model or color, on images of violations submitted by users.
	
	\item Highlight to users the areas with the highest frequency of violations and information about vehicles that commit most violations.
	
	\item Automatically identify potentially unsafe	areas crossing SafeStreets' information with accident data from the Local Police, possibly suggesting interventions.
	
	\item Send violations data to the Local Police to automatically create new traffic tickets if it can be proved that the	chain	of	custody	of	the	information	coming	from	the	users	is	never	broken.
	
	\item Generate statistics related to ticket emissions to inform users about how effective SafeStreets is.
	
\end{itemize}

On the other hand, the purpose of this paper is to define in a detailed way all the functions and requirements of the application.\\ In doing this, we start focusing on a brief overview to characterize the product with relevance to its interaction with the world, then we will proceed deeply in analysing which functions are relevant and should be provided, and which requirements are needed to the stakeholders. 
