As this document is the natural continuation of the Requirements Analysis and Specification Document, many of the definitions used in that document will be used in this Design Document.
Thus, to be fully clear and many self-explanatory as possible we include a subset of definitions taken from the Requirement Document.

\begin{itemize}
	\item \textit{Data Mining}: The process of discovering patterns in large data sets involving methods at the intersection of machine learning, statistics, and database systems.
	
	\item \textit{Report}: The data that a user has provided to the authorities that witness a violation by a vehicles.
	
	\item \textit{Ticket}: Notice issued by a law enforcement official to a motorist or other road user, indicating that the user has violated traffic laws.
	
	\item \textit{Violation}: The general infraction that a vehicle has done and that has been reported by a SafeStreets user.
	
	\begin{comment}
		\item \textit{Guest}: This actor plays the role of a person who is not registered and thus logged in.
	
		\item \textit{User}: This actor refers to the condition of a normal person (not an officer) already signed up.
		
		\item \textit{Officer} or \textit{Authority}: This actor represents a public officer that interacts with SafeStreets in some ways.
		
		\item \textit{Customer}: either a Guest or an Authority
	\end{comment}
\end{itemize}

\flushleft
Then, in this document, it will be used the following definitions.

\begin{itemize}
	\item \textit{App}: this is the abbreviation for application, in particular this term is used meaning a mobile application.
\end{itemize}